\newcommand{\treon}{
  \resumeSubheading
      {Software Engineer}{Jan 2024 – Apr 2024 (Immigrated)}
      {Treon}{Tampere, Finland}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Led QA for a new project, collaborating with dev and design teams, and product managers from inception.}
          \resumeItem{\textbullet\ Oversaw all QA aspects, including test planning, managing Jira tickets, defining metrics, and test writing.}
          \resumeItem{\textbullet\ Identified bugs pre-release and proposed changes that enhanced user experience and system architecture.}
        \resumeItem{\textbullet\ Stack: Jira, \textbf{Jenkins}, Grafana, InfluxDB, \textbf{Python}, Bash}
      \resumeSubHeadingListEnd
}

\newcommand{\tampere}{
     \resumeSubheading
      {Lab Software Engineer}{Oct 2023 – Apr 2024}
      {Tampere University - Liquid AI Project}{Tampere, Finland}
      \resumeSubHeadingList
                \resumeItem{\textbullet\ Evaluated the existing support for WebAssembly (WASM) across widely used programming languages.}
                        \resumeItem{\textbullet\  Determined the optimal \textbf{ML/AI} tools in the WebAssembly environment through benchmarking. }

                          \resumeItem{\textbullet\ Performed comparisons of key WASM runtimes in terms of performance and support levels.}
      \resumeSubHeadingListEnd
}

\newcommand{
\nokia
}{
      \resumeSubheading
      {Software Engineer Intern}{Dec 2022 – May 2023}
      {Nokia}{Tampere, Finland}
      \resumeSubHeadingList
                \resumeItem{\textbullet\ Data Collection and Analysis Platform Team, focusing on Backend using \textbf{TypeScript/Go}}
                \resumeItem{\textbullet\ Enhanced API efficiency, achieving a \textbf{20\%} improvement in load tests.}

                          \resumeItem{\textbullet\ Shifted a product to enterprise runners, cutting maintenance tasks and boosting reliability.}
          \resumeItem{\textbullet\ Gained proficiency in \textbf{OpenShift} and \textbf{Kubernetes} clusters through hands-on experience.}
      \resumeSubHeadingListEnd
}
