\newcommand{\projectJobSearch}{
\project{https://github.com/MjMoshiri/myJobSeekingAssistant}{Job Search Assistant}{LLM Microservice}
      {Python, Docker, \textbf{HuggingFace}, React, \textbf{PostgreSQL}}{     Microservices that simplify the job search process for job seekers by scanning job boards and filtering out positions that match the user's qualifications, thereby saving time in searching and evaluating job fit.}
}
\newcommand{\logLyfe}{
\project{https://github.com/MjMoshiri/log-lyfe}{Log Lyfe}{Scalable Logger}
      {Go, \textbf{Cassandra}, Docker, Make}{High-performance logging API designed for minimal dependencies, consistent reliability, and rapid scalability.}
}
\newcommand{\secondSight}{
\project{https://github.com/MjMoshiri/SecondSight}{Second Sight}{Android App}{\textbf{Kotlin}, Android Studio,\textbf{ Jetpack Compose}, Hilt, Room}
      {Time-tracking app developed in MVVM architecture, employing top native Android technologies, standards, and device compatibility settings.}
}
\newcommand{\blockChain}{
\project{https://github.com/MjMoshiri/BlockChain}{Blockchain Ecosystem}{Cryptography}{Java , Concurrency}
      {Blockchain ecosystem featuring adjustable difficulty, SHA-256 hashing, and secure data storage. Uses concurrency, thread management, synchronization, and serialization for robust performance.}
}
\newcommand{\rqm}{
\project{https://github.com/MjMoshiri/rqm}{Quote Machine}{Test Driven Development}{\textbf{TypeScript}, React, Robot Framework, SCSS, HTML}
      {Test-driven, responsive single-page application (SPA) that fetches quotes from the Quote API, and enables sharing on Twitter.}
}
\newcommand{\codeShare}{
\project{https://github.com/MjMoshiri/CodeShare}{Code Sharing Platform}{REST API}{Java, \textbf{Spring Boot}, PostgreSQL, JavaScript, HTML, CSS}
      {RESTful API-based web application for sharing code snippets, featuring syntax highlighting and customizable access settings.}
}
\newcommand{\hyperLink}{
\project{https://github.com/MjMoshiri/HyperLink-Fetcher}{HyperLink Fetcher}{Web Crawler}{Gradle, Java, Concurrency}
      {A blockchain ecosystem featuring adjustable difficulty, SHA-256 hashing, and secure data storage. It incorporates concurrency, thread management, synchronization, and serialization for robust performance.}
}